$P$ versus $NP$

### 2019-11-17 doc/manuscript.tex
Improved the result doc

We can give a certificate-based definition for $NL$ \cite{AB09}. The certificate-based definition of $NL$ assumes that a logarithmic space Turing machine has another separated read-only tape \cite{AB09}. On each step of the machine the machine's head on that tape can either stay in place or move to the right \cite{AB09}. In particular, it cannot reread any bit to the left of where the head currently is \cite{AB09}. For that reason this kind of special tape is called $``$read once$"$ \cite{AB09}.

@@

\begin{proof}
We have that $NL \subseteq LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string. Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the elements $x = yz$). Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines. Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$. However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ in some languages in $BNL$ when the prefix $y$ is the empty string, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$. Hence, we obtain that $BNL \neq NL$ by transitivity. Nevertheless, Sauerhoff has also shown that $L \subseteq BNL \subseteq NL$ \cite{MS03}. Consequently, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}

>>>>

We can give a certificate-based definition for $NL$ \cite{AB09}. The certificate-based definition of $NL$ assumes that a logarithmic space Turing machine has another separated read-only tape \cite{AB09}. On each step of the machine the machine's head on that tape can either stay in place or move to the right \cite{AB09}. In particular, it cannot reread any bit to the left of where the head currently is \cite{AB09}. For that reason this kind of special tape is called $``$read-once$"$ \cite{AB09}.

@@

\begin{proof}
We have that $NL \subseteq LNL$, because the prefix substring $y$ of an instance $x = yz$ could be the empty string. Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix substring $y$ is the empty string in the elements $x = yz$). Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines. Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$. However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ in some languages in $BNL$ when the prefix substring $y$ is the empty string, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$. Hence, we obtain that $BNL \neq NL$ by transitivity. Nevertheless, Sauerhoff has also shown that $L \subseteq BNL \subseteq NL$ \cite{MS03}. Consequently, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}

### 2019-11-17 doc/presentation.tex
Improved the result doc

We have that $NL \subseteq LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string. Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the elements $x = yz$). Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines. Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$.
\end{frame}

@@

However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ in some languages in $BNL$ when the prefix $y$ is the empty string, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$. Hence, we obtain that $BNL \neq NL$ by transitivity. Nevertheless, Sauerhoff has also shown that $L \subseteq BNL \subseteq NL$. Consequently, we prove the complexity class $L$ is not equal to $NL$.

>>>>

We have that $NL \subseteq LNL$, because the prefix substring $y$ of an instance $x = yz$ could be the empty string. Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix substring $y$ is the empty string in the elements $x = yz$). Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines. Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$.
\end{frame}

@@

However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an element $x = yz$ in some languages in $BNL$ when the prefix substring $y$ is the empty string, such that we could move strictly nondeterministically on $y$ (that would be a $``$nondeterminism at the beginning$"$) and move strictly deterministically on the nonempty string $z$. Hence, we obtain that $BNL \neq NL$ by transitivity. Nevertheless, Sauerhoff has also shown that $L \subseteq BNL \subseteq NL$. Consequently, we prove the complexity class $L$ is not equal to $NL$.
